Are rankings of financial analysts useful to investors?

### 2015-03-12 doc/paper/paper-knitr-APS.tex
some changes
same number of stocks for both TP and EPS. Results change; all-time is indifferent in terms of ann.return

Beforehand, we convert the rankings into scores as follows:
\begin{equation}
\label{eq:score}
score_{j,i}=\frac{rank_{j,i}}{\max{rank_s}}
\end{equation}

@@

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.593\% (69.401\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively 46.424\% and 40.681\% for the top and bottom terciles.

In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.729\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%). Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.893\%, 5.116\%, 1.86\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\%,  0.126\%, \ensuremath{-0.318}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.069}\% and 0.441\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

 &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
  &$middle$ & 30.7 & 47.6 & 21.7 & 100.0 \\ 
  &$bottom$ & 13.6 & 17.0 & 69.4 & 100.0 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.4 & 27.7 & 25.9 & 100.0 \\ 
  &$middle$ & 39.1 & 29.1 & 31.8 & 100.0 \\ 
  &$bottom$ & 32.7 & 26.7 & 40.7 & 100.0 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
 &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 16.861 & 0.119 \\ 
  \naive{} & 18.615 & 16.866 & 0.120 \\ 
  \default{} & 21.729 & 20.478 & 0.102 \\

@@

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
  \multicolumn{4}{l}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.893 & 13.407 & 0.102 \\ 
  \naive{} & 14.895 & 13.393 & 0.103 \\ 
  \default{} & 19.394 & 18.602 & 0.088 \\

  \end{tabularx}
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 15.719 & 14.303 & 0.098 \\ 
  \naive{} & 15.738 & 14.304 & 0.098 \\ 
  \default{} & 18.836 & 17.795 & 0.086 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  219 &  219 &  144 \\ 
  2000 &  295 &  295 &  211 \\ 
  2001 &  341 &  341 &  257 \\ 
  2002 &  374 &  374 &  299 \\ 
  2003 &  390 &  390 &  311 \\ 
  2004 &  399 &  399 &  331 \\ 
  2005 &  414 &  414 &  343 \\ 
  2006 &  421 &  421 &  344 \\ 
  2007 &  426 &  426 &  357 \\ 
  2008 &  420 &  420 &  339 \\ 
  2009 &  365 &  365 &  300 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   73 &   73 &   44 \\ 
  2000 &  257 &  257 &  185 \\ 
  2001 &  310 &  310 &  247 \\ 
  2002 &  362 &  362 &  288 \\ 
  2003 &  374 &  374 &  307 \\ 
  2004 &  385 &  385 &  318 \\ 
  2005 &  401 &  401 &  337 \\ 
  2006 &  415 &  415 &  343 \\ 
  2007 &  421 &  421 &  352 \\ 
  2008 &  422 &  422 &  349 \\ 
  2009 &  405 &  405 &  321 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   73 &   54 \\ 
  2000 &  257 &  257 &  205 \\ 
  2001 &  314 &  314 &  264 \\ 
  2002 &  368 &  368 &  308 \\ 
  2003 &  383 &  383 &  326 \\ 
  2004 &  396 &  396 &  339 \\ 
  2005 &  414 &  414 &  357 \\ 
  2006 &  429 &  429 &  365 \\ 
  2007 &  438 &  438 &  371 \\ 
  2008 &  440 &  440 &  375 \\ 
  2009 &  442 &  442 &  378 \\ 
   \midrule 
Total &  442 &  442 &  378 \\

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
 \textit{CONS} & 1.893 & 15.147 & 0.125 &  291 & 0.291 \\ 
  \textit{TP} & 5.116 & 14.593 & 0.351 &  291 & 0.314 \\ 
  \textit{EPS} & 1.860 & 15.172 & 0.123 &  209 & 0.503 \\ 
   \midrule

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
   \midrule

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & -0.069 & 15.817 & -0.004 &  290 & 0.188 \\ 
  \textit{TP} & -0.005 & 15.633 & -0.000 &  290 & 0.192 \\ 
  \textit{EPS} & 0.441 & 15.673 & 0.028 &  250 & 0.198 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 4.476 & 0.287 & 6.780 & 0.447 & 3.577 & 0.232 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.948 & 0.261 & 6.937 & 0.477 & 4.558 & 0.311 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 6.201 & 0.485 & 9.785 & 0.794 & 6.455 & 0.540 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 10.432 & 1.201 & 14.850 & 1.844 & 10.713 & 1.299 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -2.931 & -0.233 & 1.676 & 0.136 & -2.132 & -0.173 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -0.627 & -0.042 & 3.477 & 0.242 & 0.171 & 0.011 \\ 
   \midrule 
All period & -3.032 & -0.182 & 1.893 & 0.125 & 5.116 & 0.351 & 1.860 & 0.123 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 2.689 & 0.168 & 2.635 & 0.169 & 1.145 & 0.072 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 2.686 & 0.171 & 3.280 & 0.215 & 2.599 & 0.167 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.740 & 0.448 & 6.088 & 0.492 & 5.465 & 0.453 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.542 & 1.105 & 10.065 & 1.246 & 9.312 & 1.152 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.718 & -0.344 & -4.155 & -0.306 & -4.546 & -0.332 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.373 & -0.146 & -2.019 & -0.126 & -1.759 & -0.106 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.126 & 0.008 & 0.281 & 0.018 & -0.318 & -0.020 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.836 & 0.247 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.516 & 0.230 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.565 & 0.430 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.238 & 0.876 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -6.058 & -0.439 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.827 & -0.235 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
   \midrule 
All period & -3.032 & -0.182 & -0.069 & -0.004 & -0.005 & -0.000 & 0.441 & 0.028 \\

>>>>

Beforehand, we convert the rankings into scores as follows:
\begin{equation}
\label{eq:score}
score_{j,i}=\frac{rank_{j,i}}{\max{rank_i}}
\end{equation}

@@

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.769\% (69.548\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively 46.199\% and 41.09\% for the top and bottom terciles.

In the case of EPS ranking  (panel B) 48.417\% and  28.496\% ( 46.844\% and  32.399\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.944\%, 18.99\%, and 22.207\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (16.068\%, 16.095\%, and 19.343\%). Panel C shows the EPS based weighted expected returns averages (14.964\%, 14.967\%, and 19.511\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 2.247\%, 5.4\%, 1.957\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.371 against 0.149, 0.129, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\%,  0.449\%, \ensuremath{-0.361}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.028 and \ensuremath{-0.022} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.441\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.413\% and 0.441\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

 &$top$ & 67.8 & 22.0 & 10.2 & 100.0 \\ 
  &$middle$ & 29.9 & 48.2 & 22.0 & 100.0 \\ 
  &$bottom$ & 13.4 & 17.1 & 69.5 & 100.0 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
  &$middle$ & 39.2 & 29.2 & 31.7 & 100.0 \\ 
  &$bottom$ & 32.1 & 26.8 & 41.1 & 100.0 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
 &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
  &$middle$ & 48.2 & 26.2 & 25.8 & 100.2 \\ 
  &$bottom$ & 46.3 & 25.9 & 28.5 & 100.6 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.8 & 28.3 & 26.0 & 101.2 \\ 
  &$middle$ & 45.5 & 27.0 & 28.1 & 100.6 \\ 
  &$bottom$ & 42.7 & 27.6 & 32.4 & 102.7 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.944 & 17.156 & 0.119 \\ 
  \naive{} & 18.990 & 17.173 & 0.119 \\ 
  \default{} & 22.207 & 20.707 & 0.101 \\

@@

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
  \multicolumn{4}{l}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.964 & 13.449 & 0.103 \\ 
  \naive{} & 14.967 & 13.432 & 0.103 \\ 
  \default{} & 19.511 & 18.756 & 0.089 \\

  \end{tabularx}
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 16.068 & 14.522 & 0.098 \\ 
  \naive{} & 16.095 & 14.525 & 0.098 \\ 
  \default{} & 19.343 & 18.179 & 0.084 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  202 &  202 &  145 \\ 
  2000 &  269 &  269 &  211 \\ 
  2001 &  306 &  306 &  257 \\ 
  2002 &  333 &  333 &  299 \\ 
  2003 &  346 &  346 &  311 \\ 
  2004 &  351 &  351 &  331 \\ 
  2005 &  359 &  359 &  343 \\ 
  2006 &  361 &  361 &  344 \\ 
  2007 &  365 &  365 &  357 \\ 
  2008 &  361 &  361 &  339 \\ 
  2009 &  323 &  323 &  300 \\ 
   \midrule 
Total &  379 &  379 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   69 &   69 &   44 \\ 
  2000 &  235 &  235 &  186 \\ 
  2001 &  281 &  281 &  247 \\ 
  2002 &  323 &  323 &  288 \\ 
  2003 &  334 &  334 &  307 \\ 
  2004 &  341 &  341 &  318 \\ 
  2005 &  352 &  352 &  337 \\ 
  2006 &  359 &  359 &  343 \\ 
  2007 &  362 &  362 &  352 \\ 
  2008 &  361 &  361 &  349 \\ 
  2009 &  351 &  351 &  321 \\ 
   \midrule 
Total &  379 &  379 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   69 &   69 &   54 \\ 
  2000 &  235 &  235 &  205 \\ 
  2001 &  284 &  284 &  264 \\ 
  2002 &  327 &  327 &  308 \\ 
  2003 &  341 &  341 &  326 \\ 
  2004 &  350 &  350 &  339 \\ 
  2005 &  364 &  364 &  357 \\ 
  2006 &  371 &  371 &  365 \\ 
  2007 &  375 &  375 &  371 \\ 
  2008 &  377 &  377 &  375 \\ 
  2009 &  379 &  379 &  378 \\ 
   \midrule 
Total &  379 &  379 &  378 \\

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
 \textit{CONS} & 2.247 & 15.032 & 0.149 &  257 & 0.277 \\ 
  \textit{TP} & 5.400 & 14.552 & 0.371 &  257 & 0.298 \\ 
  \textit{EPS} & 1.957 & 15.145 & 0.129 &  209 & 0.501 \\ 
   \midrule

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
   \midrule

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.413 & 15.873 & 0.026 &  257 & 0.185 \\ 
  \textit{TP} & 0.441 & 15.658 & 0.028 &  257 & 0.189 \\ 
  \textit{EPS} & 0.441 & 15.702 & 0.028 &  250 & 0.198 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 5.269 & 0.343 & 7.564 & 0.509 & 3.757 & 0.245 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 4.232 & 0.280 & 7.159 & 0.496 & 4.859 & 0.335 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 6.230 & 0.504 & 9.682 & 0.816 & 6.428 & 0.537 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 10.092 & 1.180 & 14.339 & 1.817 & 10.708 & 1.296 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -3.059 & -0.245 & 1.285 & 0.103 & -2.163 & -0.174 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -0.689 & -0.046 & 3.279 & 0.225 & 0.187 & 0.012 \\ 
   \midrule 
All period & -3.032 & -0.182 & 2.247 & 0.149 & 5.400 & 0.371 & 1.957 & 0.129 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 4.702 & 0.305 & 4.367 & 0.291 & 4.204 & 0.277 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.873 & 0.253 & 4.112 & 0.278 & 4.294 & 0.286 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.774 & 0.455 & 6.045 & 0.494 & 5.997 & 0.491 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.344 & 0.881 & 8.584 & 0.964 & 8.604 & 0.972 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -6.018 & -0.432 & -5.686 & -0.412 & -5.537 & -0.402 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.700 & -0.225 & -3.337 & -0.203 & -3.186 & -0.194 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.413 & 0.026 & 0.441 & 0.028 & 0.441 & 0.028 \\
